Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-29 04_Prep_data.Rmd
Plots of AUDPC and grain yield

for(i in unique(PM_MB_means$trial_ref)){

   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
   if(any(is.na(dat1$grain_yield.t.ha.))){next}
   if(any(is.na(dat1$AUDPC_m))){next}

plot(grain_yield.t.ha. ~ AUDPC_m, data = dat1, main = paste(dat1$location[1],(dat1$year[1])),ylim = c(0,2.5) , xlim = c(0,300))
abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
points(grain_yield.t.ha. ~ AUDPC_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")

>>>>

sm2lg <- PM_MB_means%>%
   group_by(trial_ref)%>%
   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE))%>%
   arrange(TY)

for(i in sm2lg$trial_ref){
   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
   if(any(is.na(dat1$grain_yield.t.ha.))){next}
   if(any(is.na(dat1$AUDPC_m))){next}

plot(grain_yield.t.ha. ~ AUDPC_m, 
     data = dat1, main = paste(dat1$location[1],(dat1$year[1])),
     ylim = c(0,max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)), 
     xlim = c(0,max(PM_MB_means$AUDPC_m, na.rm = TRUE)))
abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
points(grain_yield.t.ha. ~ AUDPC_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")
